Recruiting Chapter

### 2020-12-19 manuscript.Rmd
copy-edit sections 1 & 2

These metaphors are useful for comparing the comparing public flagship universities to selective private colleges and universities. Selective private colleges and universities depend on patronage from affluent households (market configuration) and philanthropic interests (associational configuration) and primarily serve social reproduction rather than social mobility. Historically, public flagship universities depended on government funding associated with the national service configuration and served social mobility rather than reproduction. Since the 1980s, reductions in public funding associated with the emergence of the market configuration encourage public flagship universities to prioritize patronage from affluent households and philanthropic interests. As suggested by the adage, "he who pays the piper calls the tune," reliance on affluent private-sector interests increases the likelihood that public flagship universities -- like selective private colleges and universities -- will primarily serve social reproduction rather than social mobility.
<!-- 
The extent to which higher education serves reproduction versus redistribution is sensitive to the external funding environment because universities depend on ``patronage as a primary revenue source'' [@RN2377, p. 138]. 
-->

We argue that the recruiting behavior of colleges and universities is an indicator of organizational enrollment priorities and, in turn, the extent to which enrollment priorities serve social mobility or social reproduction. However, access to concrete data on university recruiting behaviors has been a persistent barrier to empirical research. We collected data about off-campus recruiting visits made in 2017 by "scraping" URLs (e.g., "Coming to a neighborhood near you") once per week from college/university admissions websites and -- for a sample of public research universities -- by issuing public records requests. The first study from this data collection analyzed visits made by 15 public research universities [@RN4450]. The overwhelming majority of public research universities in our sample made more out-of-state visits than in-state visits, a finding antithetical to historic mission of public universities. These out-of-state visits focused on wealthy, predominantly white schools and communities, with a disproportionate number visits to out-of-state private high schools but relatively few visits to in-state private high schools.

Building on [@RN4450], this chapter analyzes off-campus recruiting visits to private high schools made in 2017 by a sample of 25 selective private colleges and universities and 17 public research universities. We utilize social network methods and emphasize comparisons within and between public and private postsecondary institutions. Analyses are informed by two broad, related questions. First, which types of private high schools receive visits from which types of colleges and universities? Second, to what do extent colleges and universities visit private high schools that share similar characteristics with the college (e.g., geographic region, religious affiliation, academic reputation, and racial composition)?

@@

Our decision to analyze visits to private schools is motivated by the idea that recruiting from private schools largely serves social reproduction [CITE A SOCIOLOGIST]. Thus, visits to private school are antithetical to the historic "social mobility mission" of public universities [@RN2269], particularly since most private school visits by public research universities are to out-of-state schools [@RN4450]. By contrast, recruiting from private high schools is consistent with the missions of selective private colleges and universities. From this perspective, private school visits by public research universities is an example of "privatization" that serves social reproduction.  A weakness of the empirical literature on privatization in higher education is that few studies public and private colleges/universities with respect to a behavior associated with privatization [@RN4543]. By comparing public and private colleges/universities on the behavioral dimension of recruiting visits to private schools, we hope to develop new insights about the privatization of public higher education.

Finally, although private school students are more likely than public school students to come from affluent, college-educated households, the population of US private schools contains tremendous variation in religious affiliation, academic reputation, racial and socioeconomic composition, amongst other dimensions [@RN4504]. Therefore, focusing solely on visits to private schools enables us to develop a nuanced analysis of which types of private high schools receive visits from which types colleges and universities. These nuances would be dificult to observe in an analysis that also included visits to public high schools.

@@

The "enrollment funnel" -- depicted in Figure \@ref(fig:em-funnel) -- is a conceptual heuristic that identifies stages in the student recruitment process (prospects, inquiries, applicants, accepted applicants, and enrolled students). “Prospects” are “all the potential students you would want to attract to your institution” [@RN4322]. “Inquiries” are prospects that contact the institution, including those who respond to a solicitation and those who reach out on their own. The enrollment management industry uses the enrollment funnel to inform marketing and recruiting interventions that target specific stages. Most scholarship on enrollment management focuses on the final stages of the enrollment funnel, specifically which applicants are admitted and the use of financial aid "leveraging" to convert admits to enrollees [e.g., @RN3536; @RN3544; @RN3523; @RN4131; @RN2241; @RN3564; @RN1948]. By contrast, the enrollment management industry expends substantial resources on marketing/recruiting activities that target earlier stages of the enrollment funnel [@RN4664]. [SHOULD WE TRY TO ADD SOME CONCRETE NUMBERS ON $ SPENDING AT PARTICULAR UNIVERSITIES?]

Institutions identify undergraduate "prospects" by purchasing "student lists" -- containing contact, demographic, and academic achievement information -- from College Board, ACT, and other vendors. Universities control which prospects contained within a list by filtering on criteria such as zip code, test scores, and high school GPA. Once prospects and inquiries are identified, they are targeted with remote and face-to-face recruiting interventions designed to solicit applications and deepen engagement. Remote recruiting interventions include postcards, brochures, email, text messages, and targeted social media. Face-to-face recruiting interventions include on-campus visits by prospects and off-campus recruiting visits by admissions representatives to high schools, community colleges, college fairs, etc. Institutions utilize advertising (traditional and digital) and social media to solicit inquiries and to create positive "buzz" amongst prospects [@RN4411][CITE OTHER].  Given the the rise in “stealth applicants” who do not inquire before applying (Dupaul & Harris, 2012), advertising and social media enables universities to tell their story to prospects who do not wish to be contacted.

What do we know about off-campus recruiting from previous research? As is true for most aspects of enrollment management, much of what we know about off-campus recruiting comes from consulting firms (e.g., Ruffalo-Noel Levitz, EAB), professional associations (e.g., NACAC), and from practioner-oriented publications. Market research describes off-campus recruiting visits as a means of identifying prospects and deepening engagement with prospects already being targeted through mail/email [@RN4323; @RN4402; @RN4664].

@@

With respect to expenditure, Table \@ref(tab:ug-recruit-budget), reproduced from @RN4664, shows the the percentage of undergraduate recruitment budget allocated to different marketing and recruiting activities. ^[table drawn directly from @RN4664 Figure 9; based on a convenience sample of 45 four-year non-profit institutions and 21 four-year public institutions]. The average public university spent 16% of its recruiting budget on off-campus recruiting visits, compared to 12% of its budget on purchasing student lists and 17% of its budget on "prospective student communications" (e.g., mail, email, text, social media) targeting prospects and inquiries. An emergent trend over the past decade -- partially a response to public universities seeking nonresident students -- has been the growth of "regional recruiters" who target specific metropolitan areas in the US and abroad [@RN4021]. These regional recruiters may be college/university employees or they may be independent contractors who live in the metropolitan area they recruit.

@@

@RN4321 analyzed recruiting from the perspective of an elite private boarding school in order to understand "how such schools continue to get comparatively under-qualified students into top colleges and universities" (p. 98). The answer begins by considering the goals of colleges, which are represented by admissions officers, and the goals of private high schools, which are represented by guidance counselors. Colleges want high achieving students who can pay tuition and donate. They want low acceptance and high yield rates, which are important for rankings. Colleges also want a class composed of "interesting characters" whose curricular and extracurricular strengths meet the needs of important campus constituents (e.g., academic majors, the athletic department, clubs, etc.). Private high schools want to send _all_ students to the best college possible. Here, high school guidance counselors face "the pressure of making sure their school seems worth it – that \ldots paying some $40,000+, really does aid students in the college process" [@RN4321, p. 105].

@@

To explain how high school counselors capitalize on this opportunity, @RN4407 describes two hypothetical students -- Susan and Billy -- who both apply to Harvard and Yale. Susan is a shoo-in at both universities, but wants to attend Harvard. Billy has a weaker academic record than most Ivy League students, but has strong extracurricular activities. The guidance counselor tells Harvard that Susan wants to attend Harvard. Next, he informs Yale that Susan will choose Harvard, but Billy loves Yale and has great "character" and extracurricular activities. In the end, Harvard rejects Billy and accepts Susan, thereby, decreasing acceptance rate and increasing yield. Yale rejects Susan and accepts Billy, thereby, decreasing acceptance rate and increasing yield.

The horsetrading described by @RN4407 depends on a relationship where the college can trust statements made by the high school counselor and vice-versa. This relationship is the product of repeated interactions over many years. A high school that makes false statements about applicant intentions faces consequences. The college "might stop taking these telephone calls and ignore the information provided. They may even start accepting fewer students from the school, thinking it is less than an honest" [@RN4321, p. 106]. Because the college and the high school are mutually dependent, however, both "have an incentive to continue with a strong, honest relationship" [@RN4321, p. 106]. However, such horsetrading may be less pervasive than now than it was in prior decades and may be less common at non-elite private schools. Additionally, college admissions officer from public universities likely have less authority to engage in these tacit negotiations because admissions criteria at public universities face greater public scrutiny than admissions criteria at private colleges and universities.

@@

To summarize, @RN3519 finds that off-campus recruiting visits are important for the maintenance of strong relationships between a college and a high school. Strong relationships enable colleges and schools to negotiate and send trustworthy information to one another and in the absence of strong relationships it is less likely that that a college admissions counselor will "take the call" of a high school guidance counselor [@RN4321; @RN4407]. Building on these findings, we reason that the presence of a recruiting visit between a college and a high school is an indicator that the college and the high school have a relationship. First, the fact that the college made the effort to visit suggests that the college wants to enroll students from the high school. Second, the fact that the high school hosted the visit suggests that the high school likely views the college as a desirable destination for some of its students.  Third, the presence of the recruiting visit suggests the probability of additional interactions (e.g., phone calls).

Our project collected data about off-campus recruiting visits made in 2017 by a convenience sample of colleges universities. Our analysis sample is based on three different lists of postsecondary institutions: first, the set of public research universities (which category) as defined by the YYYY Carnegie Classification; second, private universities in the top 100 of USNWR YYYY "national universities"; and, third, private colleges in the top 50 of USNWR YYYY "national liberal arts colleges" rankings. For each of these institutions, we investigated their admissions website for pages that provided the details of upcoming off-campus recruiting visits. For institutions that posted such pages, we scraped the pages once per week throughout the 2017 calendar year. Many colleges and university only posted certain kinds of events (e.g., hotel receptions and national college fairs) but not others (e.g., day-time visits to high schools). These institutions are excluded from the analyses. Our final analysis sample consists of X public research universities, X private research universities, and X private liberal arts colleges. [MAYBE ADD TABLE/FIGURE OR APPENDIX TABLE/FIGURE ON CHARACTERISTICS OF INSTITUTIONS IN OUR SAMPLE?]

Our analyses to date have focused only on visits by public research universities [CITE]. The big-picture takeaways are as follows. Most public research universities in our sample made more out-of-state than in-state recruiting visits. The exceptions were UC-Berkeley, UC-Irvine, and North Carolina State University, three institutions with relatively generous state appropriations and the only three public universities in our sample that faced strong nonresident enrollment caps. Accross all universities, out-of-state visits systematically targeted affluent, predominantly white schools and communities, usually within populous metropoitan areas. Most public universities also made a disproportionate number of out-of-state visits to private high schools. Analyses of in-state visits also found that public high schools in affluent communities were more likely to receive a visit, but this relationship was modest compared to the income disparity between visited and not visited out-of-state public schools. Furthermore, in-state visits did not consistently indicate preferences for majority white high schools or for private high schools.

Figures \@ref(fig:event-count-figure-privu) and \@ref(fig:event-count-figure-pubu) show simple counts and descriptive statistics of off-campus recruiting visits by colleges and universities in our sample. TEXT BRIEFLY DESCRIBING FINDINGS FROM DESCRIPTIVE TABLES.... Table/Figure X demonstrates the disproportionate number of visits to private high schools. The goal of this chapter is to investigate off-campus recruiting visits to private high schools. Which types of private high schools receive visits from which types of colleges and universities? Additionally, to what extent were visits a college/university to a private high school more likely if the two organizations were similar to one another on key characteristics? Our analyses focus on the characteristics of academic reputation, geographic region, religious affiliation, and racial composition. WHAT TO SHOW IN TABLES/FIGURES:
<!--
- Table/figure of number of visits by visit type and in/out-of-state
- Table/figure showing disproportionate number of visits to private high schools.
-->

@@

[HOW DOES RACIAL COMPOSITION OF VISITED PRIVATE HIGH SCHOOLS COMPARE TO RACIAL COMPOSITION OF ALL PRIVATE HIGH SCHOOLS? CUT/REVISE TEXT DEPENDING ON ANSWER TO THIS QUESTION] Private high schools tend to have a higher share of White students than public high schools. Moreover, the private high schools that were visited by private colleges and universities in our sample had a lower share of Black/Latinx/Native students, on average, than the population of private high schools. Our findings suggest that the low number of Black/Latinx/Native students at private colleges and universities may be driven by thse institutions explicitly recruiting from private high schools that enroll few Black/Latinx/Native students.

>>>>

These metaphors are useful for comparing public flagship universities to selective private colleges and universities. Selective private colleges and universities depend on patronage from affluent households (market configuration) and philanthropic interests (association configuration) and primarily serve social reproduction rather than social mobility. Historically, public flagship universities depended on government funding associated with the national service configuration and served social mobility rather than reproduction. Since the 1980s, reductions in public funding associated with the emergence of the market configuration encourage public flagship universities to prioritize patronage from affluent households and philanthropic interests. As suggested by the adage, "he who pays the piper calls the tune," reliance on affluent private-sector interests increases the likelihood that public flagship universities -- like selective private colleges and universities -- will primarily serve social reproduction rather than social mobility.
<!-- 
The extent to which higher education serves reproduction versus redistribution is sensitive to the external funding environment because universities depend on ``patronage as a primary revenue source'' [@RN2377, p. 138]. 
-->

We argue that the recruiting behavior of colleges and universities is an indicator of organizational enrollment priorities and, in turn, the extent to which enrollment priorities serve social mobility or social reproduction. However, access to concrete data on university recruiting behaviors has been a persistent barrier to empirical research. We collected data on off-campus recruiting visits made in 2017 by "scraping" URLs (e.g., "Coming to a neighborhood near you") once per week from college/university admissions websites and -- for a sample of public research universities -- by issuing public records requests. The first study from this data collection analyzed visits made by 15 public research universities [@RN4450]. The overwhelming majority of public research universities in our sample made more out-of-state visits than in-state visits, a finding antithetical to historic mission of public universities. These out-of-state visits focused on wealthy, predominantly white schools and communities, with a disproportionate number of visits to out-of-state private high schools but relatively few visits to in-state private high schools.

Building on @RN4450, this chapter analyzes off-campus recruiting visits to private high schools made in 2017 by a sample of 25 selective private colleges and universities and 17 public research universities. We utilize social network methods and emphasize comparisons within and between public and private postsecondary institutions. Analyses are informed by two broad, related questions. First, which types of private high schools receive visits from which types of colleges and universities? Second, to what extent do colleges and universities visit private high schools that share similar characteristics with the college (e.g., geographic region, religious affiliation, academic reputation, and racial composition)?

@@

Our decision to analyze visits to private schools is motivated by the idea that recruiting from private schools largely serves social reproduction<!-- [CITE A SOCIOLOGIST]-->. Thus, visits to private schools are antithetical to the historic "social mobility mission" of public universities [@RN2269], particularly since most private school visits by public research universities are to out-of-state schools [@RN4450]. By contrast, recruiting from private high schools is consistent with the missions of selective private colleges and universities. From this perspective, private school visits by public research universities is an example of "privatization" that serves social reproduction.  A weakness of the empirical literature on privatization in higher education is that few studies public and private colleges/universities with respect to a behavior associated with privatization [@RN4543]. By comparing public and private colleges/universities on the behavioral dimension of recruiting visits to private schools, we hope to develop new insights about the privatization of public higher education.

Finally, although private school students are more likely than public school students to come from affluent, college-educated households, the population of US private schools contains tremendous variation in religious affiliation, academic reputation, racial and socioeconomic composition, amongst other dimensions [@RN4504]. Therefore, focusing solely on visits to private schools enables us to develop a nuanced analysis of which types of private high schools receive visits from which types of colleges and universities. These nuances would be difficult to observe in an analysis that also included visits to public high schools.

@@

The "enrollment funnel" -- depicted in Figure \@ref(fig:em-funnel) -- is a conceptual heuristic that identifies stages in the student recruitment process (prospects, inquiries, applicants, accepted applicants, and enrolled students). "Prospects" are "all the potential students you would want to attract to your institution" [@RN4322]. "Inquiries" are prospects that contact the institution, including those who respond to a solicitation and those who reach out on their own. The enrollment management industry uses the enrollment funnel to inform marketing and recruiting interventions that target specific stages. Most scholarship on enrollment management focuses on the final stages of the enrollment funnel, specifically which applicants are admitted and the use of financial aid "leveraging" to convert admits to enrollees [e.g., @RN3536; @RN3544; @RN3523; @RN4131; @RN2241; @RN3564; @RN1948]. By contrast, the enrollment management industry expends substantial resources on marketing/recruiting activities that target earlier stages of the enrollment funnel [@RN4664]. <!--[SHOULD WE TRY TO ADD SOME CONCRETE NUMBERS ON $ SPENDING AT PARTICULAR UNIVERSITIES?]-->

Institutions identify undergraduate "prospects" by purchasing "student lists" -- containing contact, demographic, and academic achievement information -- from College Board, ACT, and other vendors. Universities control which prospects are contained within a list by filtering on criteria such as zip code, test scores, and high school GPA. Once prospects and inquiries are identified, they are targeted with remote and face-to-face recruiting interventions designed to solicit applications and deepen engagement. Remote recruiting interventions include postcards, brochures, emails, text messages, and targeted social media. Face-to-face recruiting interventions include on-campus visits by prospects and off-campus recruiting visits by admissions representatives to high schools, community colleges, college fairs, etc. Institutions utilize advertising (traditional and digital) and social media to solicit inquiries and to create positive "buzz" amongst prospects [@RN4411]<!--[CITE OTHER]-->. Given the the rise in "stealth applicants" who do not inquire before applying (Dupaul & Harris, 2012), advertising and social media enables universities to tell their story to prospects who do not wish to be contacted.

What do we know about off-campus recruiting from previous research? As is true for most aspects of enrollment management, much of what we know about off-campus recruiting comes from consulting firms (e.g., Ruffalo-Noel Levitz, EAB), professional associations (e.g., NACAC), and from practitioner-oriented publications. Market research describes off-campus recruiting visits as a means of identifying prospects and deepening engagement with prospects already being targeted through mail/email [@RN4323; @RN4402; @RN4664].

@@

With respect to expenditure, Table \@ref(tab:ug-recruit-budget), reproduced from @RN4664, shows the percentage of undergraduate recruitment budget allocated to different marketing and recruiting activities.^[Table drawn directly from @RN4664 Figure 9, which is based on a convenience sample of 45 four-year non-profit institutions and 21 four-year public institutions.] The average public university spent 16% of its recruiting budget on off-campus recruiting visits, compared to 12% of its budget on purchasing student lists and 17% of its budget on "prospective student communications" (e.g., mail, email, text, social media) targeting prospects and inquiries. An emergent trend over the past decade -- partially a response to public universities seeking nonresident students -- has been the growth of "regional recruiters" who target specific metropolitan areas in the US and abroad [@RN4021]. These regional recruiters may be college/university employees or they may be independent contractors who live in the metropolitan area they recruit.

@@

@RN4321 analyzed recruiting from the perspective of an elite private boarding school in order to understand "how such schools continue to get comparatively under-qualified students into top colleges and universities" (p. 98). The answer begins by considering the goals of colleges, which are represented by admissions officers, and the goals of private high schools, which are represented by guidance counselors. Colleges want high-achieving students who can pay tuition and donate. They want low acceptance and high yield rates, which are important for rankings. Colleges also want a class composed of "interesting characters" whose curricular and extracurricular strengths meet the needs of important campus constituents (e.g., academic majors, the athletic department, clubs, etc.). Private high schools want to send _all_ students to the best college possible. Here, high school guidance counselors face "the pressure of making sure their school seems worth it – that \ldots paying some $40,000+, really does aid students in the college process" [@RN4321, p. 105].

@@

To explain how high school counselors capitalize on this opportunity, @RN4407 describes two hypothetical students -- Susan and Billy -- who both apply to Harvard and Yale. Susan is a shoo-in at both universities, but wants to attend Harvard. Billy has a weaker academic record than most Ivy League students, but has strong extracurricular activities. The guidance counselor tells Harvard that Susan wants to attend Harvard. Next, he informs Yale that Susan will choose Harvard, but Billy loves Yale and has great "character" and extracurricular activities. In the end, Harvard rejects Billy and accepts Susan, thereby, decreasing acceptance rate and increasing yield. Yale rejects Susan and accepts Billy, thereby, also decreasing acceptance rate and increasing yield.

The horsetrading described by @RN4407 depends on a relationship where the college can trust statements made by the high school counselor and vice-versa. This relationship is the product of repeated interactions over many years. A high school that makes false statements about applicant intentions faces consequences. The college "might stop taking these telephone calls and ignore the information provided. They may even start accepting fewer students from the school, thinking it is less than an honest" [@RN4321, p. 106]. Because the college and the high school are mutually dependent, however, both "have an incentive to continue with a strong, honest relationship" [@RN4321, p. 106]. Although, such horsetrading may be less pervasive now than it was in prior decades and may be less common at non-elite private schools. Additionally, college admissions officers from public universities likely have less authority to engage in these tacit negotiations because admissions criteria at public universities face greater public scrutiny than admissions criteria at private colleges and universities.

@@

To summarize, @RN3519 finds that off-campus recruiting visits are important for the maintenance of strong relationships between a college and a high school. Strong relationships enable colleges and schools to negotiate and send trustworthy information to one another. In the absence of strong relationships, it is less likely that a college admissions counselor will "take the call" of a high school guidance counselor [@RN4321; @RN4407]. Building on these findings, we reason that the presence of a recruiting visit between a college and a high school is an indicator that the college and the high school have a relationship. First, the fact that the college made the effort to visit suggests that the college wants to enroll students from the high school. Second, the fact that the high school hosted the visit suggests that the high school likely views the college as a desirable destination for some of its students.  Third, the presence of the recruiting visit suggests the probability of additional interactions (e.g., phone calls).

Our project collected data on off-campus recruiting visits made in 2017 by a convenience sample of colleges and universities. Our analysis sample is based on three different lists of postsecondary institutions: all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102); all private universities in the top 100 of U.S. News and World Report National Universities rankings (N=58); and all private colleges in the top 50 of U.S. News and World Report Liberal Arts Colleges rankings (N=47). For each of these institutions, we investigated their admissions website for pages that provided the details of upcoming off-campus recruiting visits. For institutions that posted such pages, we scraped the pages once per week throughout the 2017 calendar year. Many colleges and university only posted certain kinds of events (e.g., hotel receptions and national college fairs) but not others (e.g., day-time visits to high schools). These institutions are excluded from the analyses. Our final analysis sample consists of 17 public research universities, 13 private research universities, and 12 private liberal arts colleges. <!--[MAYBE ADD TABLE/FIGURE OR APPENDIX TABLE/FIGURE ON CHARACTERISTICS OF INSTITUTIONS IN OUR SAMPLE?]-->

Our analyses to date have focused only on visits by public research universities<!--[CITE]-->. The big-picture takeaways are as follows. Most public research universities in our sample made more out-of-state than in-state recruiting visits. The exceptions were UC Berkeley, UC Irvine, and North Carolina State University, three institutions with relatively generous state appropriations and the only three public universities in our sample that faced strong nonresident enrollment caps. Across all universities, out-of-state visits systematically targeted affluent, predominantly white schools and communities, usually within populous metropolitan areas. Most public universities also made a disproportionate number of out-of-state visits to private high schools. In addition, analyses of in-state visits found that public high schools in affluent communities were more likely to receive a visit, but this relationship was modest compared to the income disparity between visited and not visited out-of-state public schools. Furthermore, in-state visits did not consistently indicate preferences for majority white high schools or for private high schools.

Figures \@ref(fig:event-count-figure-pubu) and \@ref(fig:event-count-figure-privu) show the number of off-campus recruiting visits by public and private colleges and universities in our sample, separated by event type and in-state vs. out-of-state. <!--TEXT BRIEFLY DESCRIBING FINDINGS FROM DESCRIPTIVE TABLES.... -->Table/Figure X demonstrates the disproportionate number of visits to private high schools. The goal of this chapter is to investigate off-campus recruiting visits to private high schools. Which types of private high schools receive visits from which types of colleges and universities? Additionally, to what extent were visits by a college/university to a private high school more likely if the two organizations were similar to one another on key characteristics? Our analyses focus on the characteristics of academic reputation, geographic region, religious affiliation, and racial composition.

<!--
WHAT TO SHOW IN TABLES/FIGURES:
- Table/figure of number of visits by visit type and in/out-of-state
- Table/figure showing disproportionate number of visits to private high schools.
-->

@@

[HOW DOES RACIAL COMPOSITION OF VISITED PRIVATE HIGH SCHOOLS COMPARE TO RACIAL COMPOSITION OF ALL PRIVATE HIGH SCHOOLS? CUT/REVISE TEXT DEPENDING ON ANSWER TO THIS QUESTION] See Figure \@ref(fig:privhs-universe). Private high schools tend to have a higher share of White students than public high schools. Moreover, the private high schools that were visited by private colleges and universities in our sample had a lower share of Black/Latinx/Native students, on average, than the population of private high schools. Our findings suggest that the low number of Black/Latinx/Native students at private colleges and universities may be driven by thse institutions explicitly recruiting from private high schools that enroll few Black/Latinx/Native students.
